### 2024-06-08 basic-statistics.qmd
20240605 - getting started/load packages
20240608 - getting started
20240608 - statistical decision tree

# Base Rates {#sec-baseRates}

## Getting Started

### Load Packages

@@

>>>>

# Basic Statistics {#sec-basicStats}

## Getting Started {#sec-basicStatsGettingStarted}

### Load Packages {#sec-basicStatsLoadPackages}

@@

## Types of Data

## Statistical Decision Tree

An example statistical decision tree is depicted in Figure @fig-statisticalDecisionTree.

::: {#fig-statisticalDecisionTree}
![](images/statisticalDecisionTree.png)

A Statistical Decision Tree For Choosing an Appropriate Statistical Procedure. Obtained from: <https://commons.wikimedia.org/wiki/File:InferentialStatisticalDecisionMakingTrees.pdf>. The original source is: Corston, R., & Colman, A. M. (2000). *A crash course in SPSS for Windows*. Wiley-Blackwell.
:::
